---
title: "R Data comparison"
output: html_notebook
---

```{r}
library(boot)
library(rmarkdown)
this.dir <- paste(rstudioapi::getSourceEditorContext()$path,"/..")
setwd(this.dir)
```




# Let's see how to test similarity of two sample 1
## observing the summary and graph
We can analysis with summary,IQR,sd,boxplot,CI,T test, F test
From data analysis we can find out the different
The CI of remote and local are not even overlap.

```{r}
ci=function(x)
{
  error <- qnorm(0.975)*sd(x)/sqrt(length(x))
  m =mean(x)
  res = c(m-error,m+error)
  return(res)
  
}

data=read.csv(file="VOLTAGE.csv", header = TRUE, sep=',')

#separate the data for remote and local locations
remote=subset(data, location=="0")
local=subset(data, location=="1")

#summary Statistics of the Remote Locations
print(paste("Remot IQR:",IQR(remote$voltage),"SD",sd(remote$voltage)) )
summary(remote$voltage)
print("==================")
print(paste("Local IQR:",IQR(local$voltage),"SD",sd(local$voltage)) )
#summary Statistics of the local Locations
summary(local$voltage)

par(mfrow = c(1, 1))
boxplot(remote$voltage,local$voltage,ylab="Voltage Readings",names=c("Remote","Local"), main="Boxplots of Voltage readings")


print(paste("remot CI",ci(remote$voltage),"local CI",ci(local$voltage),"Diff CI",ci(remote$voltage-local$voltage)))

#find the 95% CI for remote, local and diff(remote,local)
#95 percent confidence interval:  0.1172284 0.6454382
#2. the CI of remote and local are not even overlap.
#the CI of diff(remote,local) is relative big


```
## test the data
```{r}
#normal qqPlots
par(mfrow=c(1,2))
#if p-value > 0.05 Normality
#remote data is non normal
shapiro.test(remote$voltage)
#local data is normal
shapiro.test(local$voltage)

#size > 26, we can run test
length(remote$voltage)

#normal data should be a slop line
par(mfrow = c(1, 2))
qqnorm(remote$voltage, main = "Remote")
qqline(remote$voltage)
qqnorm(local$voltage, main = "Local")
qqline(local$voltage)

# p value < 0.05
# They don't have same mean(reject H0)
t.test(remote$voltage, local$voltage, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# p value > 0.05
# we can't deny they have same variance(can't reject H0)
var.test(remote$voltage, local$voltage,conf.level = 0.95)

```
# Let's see how to test similarity of two sample 2
## observing the summary and graph

```{r}

data=read.csv(file="VAPOR.csv", header = TRUE, sep=',')

# boxplots
par(mfrow = c(1, 1))
boxplot(data$theoretical,data$experimental,names=c("Theoritical","Experimental"))


# histograms and QQ plots for theoritical and experimental values
par(mfrow = c(1, 2))
hist(data[,2],main="Histogram of Theoritical values", xlab = "Theoritical values")
qqnorm(data[,2])
qqline(data[,2])

hist(data[,3],main="Histogram of Experimental values", xlab = "Experimental values")
qqnorm(data[,3])
qqline(data[,3])


# histogram and QQ plot of differences
diff <- data[,2] - data[,3]

boxplot(diff, main = 'Diff')
hist(diff)
qqnorm(diff)
qqline(diff)

#observe by graph: similar



```
## test the data
Both p-value are close to 1

H0 can't be reject (theoretical = experimental)
```{r}
#oberve by t.test f.test
#two p value near 1 => almost same
t.test(data$theoretical, data$experimental, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
var.test(data$theoretical, data$experimental, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
```


```{r}
#function to calculate mean
calculated.mean <- function(x, indices) {
  result= mean(x[indices])
  return (result)
}


#the sample is small, so we do the boostrap to get the CI
#the interval is also near zero => no different
mean.boot=boot(diff,calculated.mean, R = 999, sim = "ordinary", stype = "i")
boot.ci(mean.boot,conf=0.95,type="perc") 
```

# Let's see how to test correlation of two sample
observing the temperature data
```{r}
data = read.csv(file = "bodytemp-heartrate.csv", header = TRUE, sep = ',')

data.male=subset(data, gender=="1")
data.female=subset(data, gender=="2")
par(mfrow = c(2,2))

#boxplots of body temparature vs gender
boxplot(data.male$body_temperature, data.female$body_temperature, names=c("male","female"))

#qq plots for male and female body temperature
qqnorm(data.male$body_temperature, main="Normal Q-Q Plot for males")
qqnorm(data.female$body_temperature, main="Normal Q-Q Plot for females")
```


observing the heart rate data

```{r}
par(mfrow = c(2,2))

#boxplots ofheart rate vs gender
boxplot(data.male$heart_rate, data.female$heart_rate, names=c("male","female"))

#qq plots for male and female heart rates
qqnorm(data.male$heart_rate, main="Normal Q-Q Plot for males")
qqnorm(data.female$heart_rate, main="Normal Q-Q Plot for females")

```
observing the points
```{r}
par(mfrow = c(1, 1))

#scatterplots between heart rate and body temperature for males and females
plot(body_temperature ~ heart_rate, data = data.male,ylim = range(data$body_temperature), xlim = range(data$heart_rate))
points(body_temperature ~ heart_rate, data = data.female, pch =19)
```
## test for male Correlation 
Correlation :0.1955894 

p-value = 0.1184 => correlation is equal to 0
```{r}
cor.test(data.male$body_temperature, data.male$heart_rate)
```
## test for female Correlation 
Correlation :0.2869312  

p-value = 0.02048 => correlation is not equal to 0
```{r}
cor.test(data.female$body_temperature, data.female$heart_rate)

```
## Let's do the regression and check the result for male
p-value: 0.1184 => can't reject H0 (the weight should be 0)
R-squared:  0.03826 => bad fit
Estimate 0.02326 => the weight is low which mean bad parameter
```{r}
male.reg=lm(data.male$body_temperature~data.male$heart_rate)
summary(male.reg)
```

## Let's do the regression and check the result for female
p-value  : 0.0205 => reject H0  (the weight should be not 0)

R-squared:  0.08233 => bad fit(batter than male)

Estimate 0.02632 => the weight is low which mean bad parameter
```{r}
female.reg=lm(data.female$body_temperature~data.female$heart_rate)
summary(female.reg)
```
# Over all, male and female have bad Correlation(heartbeat rate to temperture)
# But we can't reject female's heartbeat rate have correlation with temperature
